Simulation

### 2023-01-04 Quarto_Simulation/index.qmd
Remove Latex

We simulate $200$ curves (saturation regime, noise regime and linear) using $7$ points from $0$ to $200$ on the x-axis. A unique id is added for each simulated data.

@@

# Report Workflow $2$ Results

@@

Perform some data wrangling to summarise the results later. A benchmark workflow using only Pearson Correlation Coefficient with a cut off value of $0.8$ is used to compare with Workflow $2$.

@@

Results showed that Workflow $2$ is able to identify the saturated and limit of detection curves better than the benchmark workflow. On the other hand, while Workflow $2$ is able to identify less linear curves than the benchmark workflow, it gives a comparable score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Good Linearity")`

>>>>

We simulate 200 curves (saturation regime, noise regime and linear) using 7 points from 0 to 200 on the x-axis. A unique id is added for each simulated data.

@@

# Report Workflow 2 Results

@@

Perform some data wrangling to summarise the results later. A benchmark workflow using only Pearson Correlation Coefficient with a cut off value of 0.8 is used to compare with Workflow 2.

@@

Results showed that Workflow 2 is able to identify the saturated and limit of detection curves better than the benchmark workflow. On the other hand, while Workflow 2 is able to identify less linear curves than the benchmark workflow, it gives a comparable score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Good Linearity")`
